\textbf{Using the MSU Thesis Class}

### 2022-05-18 msu-thesis.tex
Added problem checklist .md file; fixed typo in docs

Previous versions of \pkg{msu-thesis} (versions 1.0--1.4b) were created for non-electronic submission and should not be used. Versions 1.5--1.6 (the first electronic submission versions) contained a |\makeabstract| command and a separate |msuabstract| environment. These have been removed as of version 1.7.  Users who are upgrading from earlier versions to version 1.7 do not need to change these commands however but their use will trigger a warning.) Version 2.0 implemented landscape pages; version 2.1 added support for \pkg{hyperref}. Versions 2.2--2.5 mainly accommodated to the ever changing whims of the MSU Graduate School. Version 2.6 fixed some appendix bugs introduced by the previous whim accommodation. Version 2.7 fixed various small spacing issues, fixed a bug which prevented a new chapter page to be a landscape page, added support for the \pkg{apacite} package, and updated degree options. Version 2.8 fixed some spacing and capitalization issues and added support for the public abstract. Version 2.9 removed subscript/superscript size restrictions, added font size options and made small spacing changes to appease the thesis office. Version 3.0 added full support for per-chapter bibliographies and appendices, and automated bibliography spacing for |natbib| and |biblatex| produced bibliographies. Version 3.1 added support for an |{algorithm}| environment and a list of algorithms to combat incompatibilities with the \pkg{algorithm} and \pkg{algorithm2e} packages.  Version 3.2 fixed some lingering problems with per-chapter appendices. Version 3.2 added code to accommodate the insane inconsistencies in formatting requirements that the thesis office requires, including a new contents option which hopefully should never be used.

>>>>

Previous versions of \pkg{msu-thesis} (versions 1.0--1.4b) were created for non-electronic submission and should not be used. Versions 1.5--1.6 (the first electronic submission versions) contained a |\makeabstract| command and a separate |msuabstract| environment. These have been removed as of version 1.7.  Users who are upgrading from earlier versions to version 1.7 do not need to change these commands however but their use will trigger a warning.) Version 2.0 implemented landscape pages; version 2.1 added support for \pkg{hyperref}. Versions 2.2--2.5 mainly accommodated to the ever changing whims of the MSU Graduate School. Version 2.6 fixed some appendix bugs introduced by the previous whim accommodation. Version 2.7 fixed various small spacing issues, fixed a bug which prevented a new chapter page to be a landscape page, added support for the \pkg{apacite} package, and updated degree options. Version 2.8 fixed some spacing and capitalization issues and added support for the public abstract. Version 2.9 removed subscript/superscript size restrictions, added font size options and made small spacing changes to appease the thesis office. Version 3.0 added full support for per-chapter bibliographies and appendices, and automated bibliography spacing for |natbib| and |biblatex| produced bibliographies. Version 3.1 added support for an |{algorithm}| environment and a list of algorithms to combat incompatibilities with the \pkg{algorithm} and \pkg{algorithm2e} packages.  Version 3.2 fixed some lingering problems with per-chapter appendices. Version 3.3 added code to accommodate the insane inconsistencies in formatting requirements that the thesis office requires, including a new contents option which hopefully should never be used.
